GeckoGraph: A Visual Language for Polymorphic Types

### 2025-10-24 response.tex

\documentclass{article}

\newcommand{\pointRaised}[2]{\medskip \noindent 
               \paragraph{#1} \textsl{#2}} 
\newcommand{\reply}{\noindent \textbf{Response}:\ }

\begin{document}

Dear Editor,

Thank you and the reviewers for the opportunity to revise our manuscript “GeckoGraph: A Visual Language for Polymorphic Types.”
We acknowledge the constructive and insightful feedback provided. We think they help improve the clarity, structure, and balance of our paper.
In this revised version, we have addressed all reviewer comments and made corresponding improvements throughout the manuscript. Below is a summary of major changes, followed by detailed point-by-point responses to each reviewer.

We hope our revisions satisfactorily address all concerns and that the paper is now suitable for publication in the Journal of Computer Languages.

Sincerely,

Authors of "GeckoGraph: A Visual Language for Polymorphic Types"

\section{Summary of Major Revisions}

\paragraph{Balanced claims} – We have now moderated the tone in the Abstract, Introduction, and Conclusion to be less ambitious and more balanced, explicitly acknowledging both the strengths and limitations of our findings.

\paragraph{Terminology refinement} – We have now replaced references to the user study as a “game” with more precise wording, such as “gamified user study” or simply “user study.”

\paragraph{New background section} – We have now added a new section, Type Systems in Functional Languages, after the Introduction to provide theoretical background and motivate the design of GeckoGraph.

\paragraph{Section structure overviews} – We have now added section structure overviews at the beginning of the Related Work and Discussion sections to better guide the reader.

\paragraph{Expanded related work} – We have now discussed the relevant study “Just TYPEical: Visualizing Common Function Type Signatures in R” to strengthen the discussion of related approaches and compare to our own contributions.

\paragraph{Enhanced discussion} – We have now improved the Discussion section with more concrete examples demonstrating the potential applications of GeckoGraph.

\paragraph{Concise figure captions} – We have shortened our figure captions throughout the manuscript for readability and stylistic consistency.

\paragraph{Improved flow between sections} – We have added a transitional paragraph linking the Design Goals and Detailed GeckoGraph Features subsections in Section 3.1.

\paragraph{Clarified explanation of type classes} – We have now refined the text in Section 3.1 to improve clarity when explaining type classes.

\paragraph{Removed unused figure} – We removed Figure 4 from the previous version, as it did not add new information to the paper.

\paragraph{Cosmetic and consistency edits} – We improved our grammar, spelling, LaTeX syntax, and overall logical coherence across the manuscript.

\section{Detailed Responses to Reviewers
Response to Reviewer 1}

\pointRaised{Comment 1:}{ The manuscript’s tone in the abstract and conclusion appears overly strong given the presented evidence.}

\reply We appreciate this observation. We have moderated the language in the Abstract, Introduction, and Conclusion to ensure our claims are proportionate to the results, and to present both positive and negative aspects of our findings.

\pointRaised{Comment 2:}{The term “game” used to describe the user study could be misleading.}

\reply We agree that we don't meet all the expectations for a game, and it's more appropriate to frame it as "an entertaining coding challenge". We changed our word of choice for “game” to “gamified user study” or simply, “user study”.

\pointRaised{Comment 3:}{The paper lacks sufficient background on type systems in functional languages.}

\reply We have added a new section titled Type Systems in Functional Languages immediately following the Introduction. This section introduces relevant concepts and better motivates the design of GeckoGraph.

\pointRaised{Comment 4:}{Please clarify the explanation of type classes.}

\reply The subsection explaining type classes (Section 3.1) has been rewritten for clarity, with simpler language and improved examples.

\section{Response to Reviewer 2}

\pointRaised{Comment 1:}{The related work section could benefit from additional references and a clearer structure.}

\reply We have expanded the Related Work section to include “Just TYPEical: Visualizing Common Function Type Signatures in R” and added an introductory overview to outline its structure.

\pointRaised{Comment 2:}{The discussion section is abstract and lacks concrete examples.}

\reply We have revised the Discussion section to include several new examples illustrating potential applications of GeckoGraph.

\pointRaised{Comment 3:}{Some figures and captions are overly detailed.}

\reply We have shortened all figure captions for conciseness and removed Figure 4 from the earlier version, as it did not contribute additional insight.

\pointRaised{omment 4:}{The paper’s flow between sections feels abrupt.}

\reply We added a transitional paragraph between the Design Goals and Detailed GeckoGraph Features sections to improve narrative flow.

\pointRaised{Comment 5:}{Minor issues with grammar, formatting, and coherence.}

\reply We have now carefully proofread the entire manuscript, correcting grammatical errors, LaTeX syntax issues, and improving overall readability.

\end{document}

### 2025-10-25 response.tex

Thank you and the reviewers for the opportunity to revise our manuscript “GeckoGraph: A Visual Language for Polymorphic Types.”
We acknowledge the constructive and insightful feedback provided. We think they help improve the clarity, structure, and balance of our paper.
In this revised version, we have addressed all reviewer comments and made corresponding improvements throughout the manuscript. Below is a summary of major changes, followed by detailed point-by-point responses to each reviewer.

We hope our revisions satisfactorily address all concerns and that the paper is now suitable for publication in the Journal of Computer Languages.

Sincerely,

Authors of "GeckoGraph: A Visual Language for Polymorphic Types"
\section{Summary of Major Revisions}

\paragraph{Balanced claims} We have moderated the tone in the \textit{Abstract}, \textit{Introduction}, and \textit{Conclusion} to present a more balanced and evidence-based discussion, explicitly acknowledging both the strengths and limitations of our findings.

\paragraph{Terminology refinement} We have replaced references to the user study as a “game” with more accurate terms such as “gamified user study” or simply “user study,” to avoid overstating the level of interactivity.

\paragraph{New background section} We have added a new section, \textit{Type Systems in Functional Languages}, following the \textit{Introduction} to provide theoretical background and better motivate the design of GeckoGraph.

\paragraph{Section structure overviews} We have introduced short structural overviews at the beginning of the \textit{Related Work} and \textit{Discussion} sections to help guide readers through their organization.

\paragraph{Expanded related work} We have extended the \textit{Related Work} section to include additional references, notably the paper “Just TYPEical: Visualizing Common Function Type Signatures in R,” and used it to better position GeckoGraph among related visualization approaches.

\paragraph{Enhanced discussion} The \textit{Discussion} section has been revised to include more concrete examples demonstrating potential applications of GeckoGraph.

\paragraph{Concise figure captions} All figure captions have been shortened for clarity, readability, and stylistic consistency.

\paragraph{Improved flow between sections} A transitional paragraph has been added to connect the \textit{Design Goals} and \textit{Detailed GeckoGraph Features} subsections in Section~3.1, improving the logical flow of ideas.

\paragraph{Clarified explanation of type classes} The explanation of type classes in Section~3.1 has been rewritten in simpler language with improved examples. Figure~3 now includes concrete illustrations to support the description.

\paragraph{Removed unused figure} We removed the previous Figure~4, as it did not contribute additional information to the paper.

\paragraph{Cosmetic and consistency edits} Grammar, spelling, LaTeX syntax, and stylistic consistency have been carefully reviewed and corrected throughout the manuscript.

\section{Detailed Responses to Reviewers}

\subsection*{Response to Reviewer 1}

\pointRaised{Comment 1:}{The manuscript’s tone in the abstract and conclusion appears overly strong given the presented evidence.}

\reply We appreciate this observation. The language in the \textit{Abstract}, \textit{Introduction}, and \textit{Conclusion} has been moderated to ensure that claims are proportionate to the results and that both positive and negative aspects of our findings are clearly presented.

@@

\pointRaised{Comment 2:}{The term “game” used to describe the user study could be misleading.}

\reply We agree. The tasks in our study do not fully meet the criteria for a “game.” We now describe it more accurately as a “gamified user study” or simply a “user study,” emphasizing its educational and experimental nature.

\pointRaised{Comment 3:}{Please clarify the explanation of type classes.}

\reply The subsection on type classes (Section~3.1) has been rewritten for clarity and supported by clearer examples. Figure~3 has also been improved to include illustrative examples that reinforce our description of GeckoGraph.

\pointRaised{Comment 4:}{Issues with figures and references.}

\reply The previous Figure~4 has been removed. Incorrect cross-references such as “Fig.~2.2” have been corrected (now “Fig.~8”). Repetitions such as “Appendix Appendix~A” have been fixed.

\pointRaised{Comment 5:}{Temper the narrative of qualitative results—the data show neutral user opinions.}

\reply We have clarified the neutrality of participants’ overall feedback and added clearer indicators of sentiment (e.g., “slightly positive,” “moderately negative”) to reflect the scale values more accurately.

\pointRaised{Comment 6:}{Clarify speculative claims in the Discussion.}

\reply We now explicitly mark speculative interpretations in Section~6 (\textit{Discussion}) with leading phrases such as “We hypothesize that...”.

\pointRaised{Comment 7:}{Wording and grammar issues.}

\reply We have corrected numerous stylistic and grammatical errors, including:
“expressiveness power” → “expressiveness”,
“high-order function” → “higher-order function”,
and “GechoGraph” → “GeckoGraph.”  
Unclear terms such as “tangibly” and “regular higher-order function” have been clarified or replaced with precise expressions and supported with examples.  
We also removed unnecessary spaces before footnote labels.

\subsection*{Response to Reviewer 2}

\pointRaised{Comment 1:}{The paper lacks sufficient background on type systems in functional languages.}

\reply We have added a new section titled \textit{Type Systems in Functional Languages} immediately after the \textit{Introduction}. This section introduces key theoretical concepts and motivates the design rationale for GeckoGraph.

\pointRaised{Comment 2:}{The related work section could benefit from additional references and a clearer structure.}

\reply We have expanded and reorganized the \textit{Related Work} section, including new references such as “Just TYPEical: Visualizing Common Function Type Signatures in R.” A short overview paragraph now outlines the section’s structure and focus.

\pointRaised{Comment 3:}{The discussion section is abstract and lacks concrete examples.}

\reply We have revised the \textit{Discussion} section to include additional examples illustrating practical applications of GeckoGraph. Figure~14 has been added to support this discussion.

\pointRaised{Comment 4:}{Begin Sec.~5 (“Discussion”) and Sec.~6 (“Related Work”) with overview paragraphs explaining purpose and structure.}

\reply Overview paragraphs have been added at the start of both sections to help orient readers and clarify how each section is organized.

\pointRaised{Comment 5:}{Usage of figures.Some figures (1,3,10,14 previous version) captions are too long. Figure 4 is hard to understand and its purpose is unclear.}

\reply Long figure captions have been shortened for conciseness. The previous Figure~4, which did not contribute new insights, has been removed.

\pointRaised{Comment 6:}{The paper’s flow between sections feels abrupt.}

\reply We have added a transitional paragraph between the \textit{Design Goals} and \textit{Detailed GeckoGraph Features} subsections in Section~3 to improve the narrative flow.

\pointRaised{Comment 7:}{Minor issues with grammar, formatting, and coherence.}

\reply The manuscript has been carefully proofread to correct grammatical and LaTeX syntax errors and improve readability.  
Examples include correcting figure references (e.g., “Fig.~2.2” → “Fig.~8”), fixing duplicate words (“Appendix Appendix~A” → “Appendix~A”), and removing extra spaces before footnote labels.

\pointRaised{Comment 8:}{Clarify user tasks and results in Figures 9 and 10.}

\reply We have clarified that the user in Figures~9 and~10 did not reach the correct solution and explained how GeckoGraph’s visual feedback can help identify and correct such mistakes. We also fixed a typo in Figure~9, changing “runHero z” to “runZero z.”

\pointRaised{Comment 9:}{Clarify whether participants indicate their experience once or before each run.}

\reply We clarified that participants report their programming experience once, before beginning the tasks.

\pointRaised{Comment 10:}{Distinguish between empirical findings and authors’ interpretations in the Discussion.}

\reply We now explicitly distinguish between observed results and speculative interpretations in the \textit{Discussion}, using clear phrases such as “We hypothesize that...” to signal interpretive commentary.

\pointRaised{Comment 10:}{Add reference for “between-subject design.”}

\reply We now correctly cite Fisher, R.A. {\it The Design of Experiements} for the phase "between-subject design."

### 2025-10-25 main.tex
More changes

%% Abstract
\begin{abstract}
Polymorphic type is an important feature in most strongly typed programming languages. They allow functions to be written in a way that can be used with different data types, while still enforcing the relationship and constraints between the values. However, programmers often find polymorphic types difficult to use and understand, and tend to reason with a mindset of concrete types. We propose GeckoGraph, a graphical notation for types. GeckoGraph aims to complement traditional text-based type notation by making reading, understanding, and comparing types easier. We conducted a large-scale user study using GeckoGraph, comparing it to text-based type notation. To our knowledge, this is the largest controlled user study on functional programming ever conducted. 
The results show no overall significant differences in task completion time or success rate. However, we observed a modest improvement in success rate among beginner participants. For the most challenging task, GeckoGraph improved success rates by 14.5\% for beginners and 11.2\% for less experienced users. These findings suggest that GeckoGraph has potential as a teaching and learning aid for polymorphic type systems.
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In programming languages, a polymorphic type \cite{Cardelli1987-fp} can represent values of different types while providing an interface to describe common behaviors for those values. Polymorphic types are one of the oldest topics in programming language theory \cite{Cardelli1987-fp}. They are central to the succinctness of statically-typed languages, while also enabling a high degree of type-safe abstraction and reusability. Polymorphic types are available in many programming languages, from functional languages such as Haskell and ML to imperative and multi-paradigm languages such as Rust\cite{Klabnik_undated-wx} and Go\cite{Griesemer_undated-ff}.

@@

While promoting robustness and code reusability, polymorphic types present challenges in learning and comprehension, particularly for novice users \cite{Jun2000-ec, Jun2000-yu}; as it is often argued that the expressiveness power of type systems often comes at the cost of their usability~\cite{Hage2020-hg}. Research indicates that humans tend to focus on concrete types and rely on polymorphic type checking only as a last resort. Moreover, polymorphic types often complicate type error usability. During type checking, compilers frequently generate new polymorphic type variables temporarily. These variables are typically discarded after type checking unless a type error occurs, in which case they are referenced in error messages. Consequently, programmers often face the task of resolving type errors involving type variables they did not explicitly author (Fig. \ref{fig:example-foldable}). Unfortunately, not many studies focus on the \textit{usability} of polymorphic types.

@@

 We aim to investigate the challenges of using polymorphic types and explore how to improve their usability with visualization and modern Human-Computer Interaction (HCI) techniques. In this paper, we propose GeckoGraph, a graphical notation for types. GeckoGraph aims to complement traditional text-based type notation and make reading, understanding, and comparing types easier. GeckoGraph is prototyped and verified iteratively, leading to a design with visual clarity applicable to many programming contexts. 
 To evaluate its effectiveness, we conducted a large-scale user study comparing GeckoGraph with standard text-based type notation. To our knowledge, this represents the largest controlled user study on functional programming to date.
The results show no overall significant differences in task completion time or success rate. However, we observed a modest improvement in success rate among beginner participants. For the most challenging task, GeckoGraph improved success rates by 14.5\% for beginners and 11.2\% for less experienced users. These findings suggest that GeckoGraph has potential as a teaching and learning aid for polymorphic type systems.

\section{Type Systems in Functional Programming}

@@

\section{GeckoGraph}

@@

Participants are assigned to one of two groups (A and B). The experiment uses a between-subjects design.  The tasks assigned to the two groups are the same. All participants receive both treatments (with and without GeckoGraph) during their runs, but in a different order.   {\bf Group A} is assisted by GeckoGraph on even levels and text-based type annotation on odd levels. {\it Group B} is assisted by text-based type annotation on even levels and GeckoGraph on odd levels. The number of participants in the two groups is counterbalanced.

@@

\section{Results}

@@

This section discusses the main findings and implications of our study. 
We begin by outlining the strengths of GeckoGraph observed from both quantitative and qualitative results (Section~\ref{sec:discussion:strengths}). 
We then discuss the limitations of the current design (Section~\ref{sec:discussion:weaknesses}) and reflect on the gamified nature of our user study (Section~\ref{sec:discussion:gamification}). 
Finally, we identify potential applications of GeckoGraph in programming tools, documentation, and education (Section~\ref{sec:discussion:applications}).

\subsection{Strengths}\label{sec:discussion:strengths}
Overall, our experimental results show no statistically significant difference in task completion time between conditions with and without GeckoGraph. However, we find that using GeckoGraph shows a significant albeit moderate effect on the task success rates for beginners. Particularly, in the hardest task (task 10), GeckoGraph improved the success rates across the two less experienced user groups by 14.5\% and 11.2\%, respectively. 
To interpret the observed advantages, we discuss the practical benefits that GeckoGraph offers to programmers.

@@

\subsubsection{Programming Assistance}
Post-study feedback highlighted a strong interest in integrating GeckoGraph into programming environments. 
Modern IDEs already allow users to inspect expression types via hover tooltips; GeckoGraph could enhance this feature by visualizing type structures directly in the tooltip. 
Similarly, GeckoGraph could be used to visualize mismatched parts of conflicting types during compilation errors, as illustrated in Fig.~\ref{fig:example-foldable}.

@@

\section{Related work}
This section reviews prior work in three areas relevant to this research. First, we examine approaches to the visualization of types in programming languages. 
We then broaden our view to general visualization techniques applied to programming environments, including topics like memory allocation and change history. Finally, we review studies comparing visual and textual representations in programming education and environments.

@@

\section{Conclusion and Future Work}
In this paper, we propose GeckoGraph, a graphical notation for type annotations in functional programming languages. GeckoGraph aims to complement traditional text-based type notation by making reading, understanding, and comparing types easier. We conducted a large-scale human study using GeckoGraph, comparing it to text-based type notation. This is the largest user study on functional programming we are aware of. Although no significant effect was found on the overall time to complete each programming task, we found a modest effect on the success rate in the beginner group. In one of the more difficult programming tasks, we find that GeckoGraph significantly improves the success rate by 14.5\% for beginners and 11.2\% for less experienced programmers.

>>>>

%% Abstract
\begin{abstract}
Polymorphic type is an important feature in most strongly typed programming languages. They allow functions to be written in a way that can be used with different data types, while still enforcing the relationship and constraints between the values. However, programmers often find polymorphic types difficult to use and understand, and tend to reason in terms of concrete types. We propose GeckoGraph, a graphical notation for types. GeckoGraph aims to complement traditional text-based type notation by making reading, understanding, and comparing types easier. We conducted a large-scale user study comparing GeckoGraph to text-based type notation. To our knowledge, this is the largest controlled user study on functional programming ever conducted. 
The results show no overall significant differences in task completion time or success rate. However, we observed a modest improvement in success rate among beginner participants. For the most challenging task, GeckoGraph improved success rates by 14.5\% for beginners and 11.2\% for less experienced users. These findings suggest that GeckoGraph has potential as a teaching and learning aid for polymorphic type systems.
\end{abstract}

@@

\section{Introduction} \label{sec:intro}
In programming languages, a polymorphic type \cite{Cardelli1987-fp} can represent values of different types while providing an interface to describe common behaviors for those values. Polymorphic types are one of the oldest topics in programming language theory \cite{Cardelli1987-fp}. They are central to the succinctness of statically typed languages while also enabling a high degree of type-safe abstraction and reusability. Polymorphic types are available in many programming languages, from functional languages such as Haskell and ML to imperative and multi-paradigm languages such as Rust\cite{Klabnik_undated-wx} and Go\cite{Griesemer_undated-ff}.

@@

While promoting robustness and code reusability, polymorphic types present challenges in learning and comprehension, particularly for novice users \cite{Jun2000-ec, Jun2000-yu}; as it is often argued that the expressiveness of type systems often comes at the cost of their usability~\cite{Hage2020-hg}. Research indicates that humans tend to focus on concrete types and rely on polymorphic type checking only as a last resort. Moreover, polymorphic types often complicate the usability of type errors. During type checking, compilers frequently generate new polymorphic type variables temporarily. These variables are typically discarded after type checking unless a type error occurs, in which case they are referenced in error messages. Consequently, programmers often face the task of resolving type errors involving type variables they did not explicitly author (Fig. \ref{fig:example-foldable}). Unfortunately, not many studies focus on the \textit{usability} of polymorphic types.

@@

 We aim to investigate the challenges of using polymorphic types and explore how to improve their usability with visualization and modern Human-Computer Interaction (HCI) techniques. In this paper, we propose GeckoGraph, a graphical notation for types. GeckoGraph aims to complement traditional text-based type notation and make reading, understanding, and comparing types easier. GeckoGraph is prototyped and iteratively verified, resulting in a design with visual clarity applicable across many programming contexts. 
 To evaluate its effectiveness, we conducted a large-scale user study comparing GeckoGraph with standard text-based type notation. To our knowledge, this represents the largest controlled user study on functional programming to date.
The results show no overall significant differences in task completion time or success rate. However, we observed a modest improvement in success rate among beginner participants. For the most challenging task, GeckoGraph improved success rates by 14.5\% for beginners and 11.2\% for less experienced users. These findings suggest that GeckoGraph has potential as a teaching and learning aid for polymorphic type systems.

% In Section~\ref{sec:type-systems}, we review key type system features in functional programming languages, many of which have recently been adopted by object-oriented and multi-paradigm languages. We highlight how these features enable flexible abstraction and expressive type modeling, while sometimes hindering usability for beginners. Section~\ref{sec:gecko-graph} presents the design of GeckoGraph, illustrating how it visualizes complex type-level information that is often implicit or hard to interpret textually. Section~\ref{sec:evaluation} describes our user study, ZeroToHero, a series of 10 programming challenges, along with the study design, recruitment, and hypotheses. Section~\ref{sec:results} reports quantitative and qualitative findings, including completion time, success rates, and participant feedback. In Section~\ref{sec:discussion}, we interpret these results, discuss GeckoGraph’s benefits and usability challenges, and explore potential applications. Section~\ref{sec:related-work} reviews related visualization research, and Section~\ref{sec:conclusion} summarizes our contributions and outlines future directions.

\section{Type Systems in Functional Programming} \label{sec:type-systems}

@@

\section{GeckoGraph} \label{sec:gecko-graph}

@@

Participants are assigned to one of two groups (A and B). The experiment uses between-subjects design \cite{Fisher1949-fn}.  The tasks assigned to the two groups are the same. All participants receive both treatments (with and without GeckoGraph) during their runs, but in a different order.   {\bf Group A} is assisted by GeckoGraph on even levels and text-based type annotation on odd levels. {\it Group B} is assisted by text-based type annotation on even levels and GeckoGraph on odd levels. The number of participants in the two groups is counterbalanced.

@@

\section{Results} \label{sec:results}

@@

This section discusses the main findings and implications of our study. 
We speculate the strengths of GeckoGraph observed from both quantitative and qualitative results (Section~\ref{sec:discussion:strengths}). 
We then discuss the limitations of the current design (Section~\ref{sec:discussion:weaknesses}) and reflect on the gamified nature of our user study (Section~\ref{sec:discussion:gamification}). 
Finally, we identify potential applications of GeckoGraph in programming tools, documentation, and education (Section~\ref{sec:discussion:applications}).

\subsection{Strengths}\label{sec:discussion:strengths}
Overall, our experimental results show no statistically significant difference in task completion time between conditions with and without GeckoGraph. However, we find that using GeckoGraph shows a significant, albeit moderate, effect on task success rates for beginners. In particular, on the hardest task (task 10), GeckoGraph improved the success rates across the two less experienced user groups by 14.5\% and 11.2\%, respectively. 
To interpret the observed advantages, we hypothesize the practical benefits that GeckoGraph offers to programmers.

@@

\subsubsection{Programming Assistance}
Post-study feedback highlighted a strong interest in integrating GeckoGraph into programming environments. 
Modern IDEs already allow users to inspect expression types via hover tooltips; GeckoGraph could enhance this feature by visualizing type structures directly in the tooltip, as envisioned in Fig.~\ref{fig:application} (Left). 
Similarly, GeckoGraph could be used to visualize mismatched parts of conflicting types during compilation errors, as illustrated in Fig.~\ref{fig:application} (Right).

\begin{figure}[]
  \includegraphics[width=\linewidth]{figures/Application.png}
  \caption{\label{fig:application} 
 {\bf Envisioning GeckoGraph as programming assistance}. (Left) Display GeckoGraph as type hints; (Right) Visualize mismatched types with GeckoGraph. }
\end{figure}

@@

\section{Related work} \label{sec:related-work}
This section reviews prior work in three areas relevant to this research. First, we examine approaches to the visualization of types in programming languages. 
We then broaden our view to general visualization techniques applied to programming environments, including topics like memory allocation and change history. Finally, we review studies comparing visual and textual representations in programming education and environments.

@@

\section{Conclusion and Future Work} \label{sec:conclusion}
In this paper, we propose GeckoGraph, a graphical notation for type annotations in functional programming languages. GeckoGraph aims to complement traditional text-based type notation by making reading, understanding, and comparing types easier. We conducted a large-scale human study using GeckoGraph, comparing it to text-based type notation. This is the largest user study on functional programming we are aware of. Although no significant effect was found on the overall time to complete each programming task, we found a modest effect on the success rate in the beginner group. In one of the more difficult programming tasks, we find that GeckoGraph significantly improves the success rate by 14.5\% for beginners and 11.2\% for less experienced programmers.
